Mix of PD and BoS

### 2022-05-05 code/mixed.Rmd
work on analysis

- would be better to have game type coded as "gametype" to avoid namespace collision
- TODO: trends over game time!
- TODO: transcript reading
- TODO: game time & feedback

@@

study1_loc="data/study1_220107"
#image_location="write-ups/images"

@@

rounds <- study1.rounds %>% union(study2.rounds)
chat <- study1.chat %>% union(study2.chat)
```
# Summary of expts
All expts reported here are from pairs of participants who played 40 rounds of a game-theory type game. At the start, each pair had 3 minutes of free chat, and then played the game. In exp 1, pairs were assigned to either all-PD or all-BoS games crossed with either access to the chat during the game or not.

@@

ggplot(bonuses, aes(x=str_c(mix," ",chat_cond), y=payoff, color=chat_cond))+geom_jitter(width=.1)+
  facet_grid(.~gametype)+
  labs(y="mean_reward", x="condition")+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+theme(legend.position = "none")+scale_y_continuous(limits=c(0,6))
```

@@

ggplot(prechat, aes(x=str_c(game_cond," ",chat_cond), y=words))+geom_jitter(width=.1, color="lightblue")+ stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+theme(legend.position = "none")+labs(y="pre-chat words / player", x="game type")
```

@@

ggplot(chat_by_pair, aes(x=repNum, y=words, color=gametype))+geom_jitter(width=.1, size=1, alpha=.2)+facet_grid(mix~gametype)+scale_y_continuous(limits=c(0,30))+
  geom_smooth()+
  labs(title="Words produced per round per game", y="words")

ggplot(is_chat, aes(x=repNum, y=pct_chat, color=gametype))+geom_point()+
  facet_grid(gametype~mix)+
  labs(y="pct of games who said anything each round")
```

@@

ggplot(success, aes(x=mean_chat, y=mean_payout, color=gametype))+geom_point()+facet_wrap(~mix)

@@

>>>>

- would be better to have game type coded as "gametype" to avoid namespace collision
- TODO: trends over game time!
- TODO: game time & feedback

@@

study1_loc="data/study1_220107"
image_location="write-ups/images"

@@

rounds <- study1.rounds %>% union(study2.rounds)
chat <- study1.chat %>% union(study2.chat)

study1.exit <- read_csv(here(study1_loc,"exit.csv"))

study2.exit <- read_csv(here(data_location, "exit.csv"))

s1 <- read_csv(here(study1_loc,"raw_results.csv")) %>% 
  select(chat_cond, game_cond, playerId) 
players <- read_csv(here(data_location,"raw_results.csv")) %>% 
  select(chat_cond, game_cond, playerId) %>% union(s1) %>% 
  unique()
exit <- study1.exit %>% union(study2.exit) %>% inner_join(players)
```
# Summary of expts
All expts reported here are from pairs of participants who played 40 rounds of a game-theory type game. At the start, each pair had 3 minutes of free chat, and then played the game. In exp 1, pairs were assigned to either all-PD or all-BoS games crossed with either access to the chat during the game or not.

@@

ggplot(bonuses, aes(x=str_c(mix,"\n",chat_cond), y=payoff, color=str_c(mix," ",chat_cond)))+geom_jitter(width=.1, alpha=.5)+
  facet_grid(.~gametype)+
  scale_color_viridis(discrete=T)+
  labs(y="mean_reward", x="condition")+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.7,color="black")+theme(legend.position = "none")+coord_cartesian(ylim=c(0,6))+labs(y="Mean reward / trial")+
    theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=14),
        strip.text=element_text(size=14) )

ggsave(here(image_location, 'payoff.png'), width=6, height=3.5, device="png", type="cairo-png")
```

@@

ggplot(prechat, aes(x=str_c(game_cond,"\n",chat_cond), y=words))+geom_jitter(width=.1, color="lightblue")+ stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+theme(legend.position = "none")+labs(y="Pre-chat words / player", x="")+
      theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=14),
        strip.text=element_text(size=14) )

ggsave(here(image_location, 'prechat.png'), width=6, height=3.5, device="png", type="cairo-png")
```

@@

ggplot(chat_by_pair, aes(x=repNum, y=words, color=gametype))+geom_jitter(width=.1, size=1, alpha=.2)+facet_grid(mix~gametype)+coord_cartesian(ylim=c(0,15))+
  geom_smooth()+
      theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=14),
        strip.text=element_text(size=14),
        legend.position = "none")+labs(y="Words / pair / trial", x="Trial number")

ggsave(here(image_location, 'words.png'), width=5, height=3.5, device="png", type="cairo-png")

```{r}
ggplot(is_chat, aes(x=repNum, y=pct_chat, color=gametype))+geom_point()+
  facet_grid(gametype~mix)+
  labs(y="pct of games who said anything each round")
```

```{r}
# per game
chatty <- game_chat %>% group_by(gameId, playerId, gametype,  mix, repNum) %>% mutate(did.chat=ifelse(words>0, 1,0))

game_chatty <- chatty %>% group_by(gameId, gametype,mix, repNum)
```

@@

ggplot(success, aes(x=mean_chat, y=mean_payout, color=gametype))+geom_point()+facet_wrap(~mix)+geom_smooth(method="lm")

@@

# But what about language?

game_chat <- chat %>% filter(chat_cond=="chat") %>% filter(!is.na(targets)) %>% select(-type) %>% left_join(rounds) %>% filter(!is.na(text)) %>% select(gameId,playerId, gametype,mix,repNum,text)

per_game <- chat %>% filter(chat_cond=="chat") %>% filter(!is.na(targets)) %>% select(-type) %>% left_join(rounds) %>% filter(!is.na(text)) %>% select(gameId,role, gametype,mix,repNum,text) %>%  mutate(game_cond=ifelse(mix=="pure", gametype, "mix"),
         words=str_count(text, "\\w+") %|% int(0)) %>% 
  filter(words>0) %>% 
  group_by(gameId,role,game_cond) %>% summarize(total_words=sum(words),total_utts=n()) %>% 
  pivot_wider(names_from=role, values_from=c(total_words, total_utts), values_fill=0) %>% 
  mutate(words_1=max(total_words_p1, total_words_p2),
         words_2=min(total_words_p1, total_words_p2),
         utts_1=max(total_utts_p1, total_utts_p2),
         utts_2=min(total_utts_p1, total_utts_p2))

words <- per_game %>% ungroup() %>% group_by(game_cond) %>% 
  select(gameId,game_cond, total_words_p1, total_words_p2) %>% 
  mutate(total=total_words_p1+total_words_p2,
         n=row_number()) %>% 
  pivot_longer(total_words_p1:total_words_p2)

  ggplot(words,aes(x=reorder(n,total),y=value, fill=name))+geom_col()+facet_grid(game_cond~.)
```

So, types of language that could occur:
- chitchat 
- negotiation about strategy/ who gets to pick
- someone naming / proposing a color to choose 
- agreement / "ok"
- other: discussion of mistakes, etc

Could hand code a bunch of this -- spelling correction might be good for detecting color words!
```{r}
color_words <- c("red","blue", "green","pink","yellow","gray","grey","salmon","cyan","purple",
                 "orange","white","brown","rose")

agreement <- c("ok","yup","yes","yep","yea","okay")
color_coded <- game_chat %>% select(text) %>%
  mutate(has.color=str_detect(text, regex(paste(color_words, collapse="|"), ignore_case=T)),
         is.color=ifelse(str_replace_all(text, "[^[:alnum:]]", "") %>% str_to_lower() %in% color_words, T,F),
         is.ok = ifelse(str_replace_all(text, "[^[:alnum:]]", "") %>% str_to_lower() %in% agreement, T,F))

color_coded %>% group_by(has.color,is.ok, is.color) %>% tally()
```

```{r}
agreement <- c("ok","yup","yes","yep","yea","okay")

color_pure <- read_csv(here("data/colorpure.csv"), guess_max = 2000) %>% mutate(gametype=game_cond)
color_mixed <- read_csv(here("data/colormixed.csv"), guess_max=2000)

color <- color_pure %>% union(color_mixed) %>% filter(!is.na(targets)) %>% filter(!is.na(text)) %>% 
  mutate(is.color=ifelse(is.na(color),0,1), 
         is.num= ifelse(str_detect(text, regex("[0-9]", ignore_case=T)),1,0),
         is.ok = ifelse(str_replace_all(text, "[^[:alnum:]]", "") %>% str_to_lower() %in% agreement, 1,0)) %>% group_by(game_cond) %>% summarize(c=mean(is.color),num=mean(is.num),ok=mean(is.ok), total=n())
```
# Are they human?

```{r bot}

exit %>% 
  group_by(game_cond, chat_cond, human) %>% 
  tally() %>% 
  pivot_wider(names_from=human, values_from=n) %>% 
  mutate(pct=yes/(no+yes))
